---
title: "Using shinyypr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using shinyypr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

`shinyypr` is an R package to run a user interface to the [ypr](https://github.com/poissonconsulting/ypr) R package. [ypr](https://github.com/poissonconsulting/ypr) implements equilibrium-based yield per recruit methods for estimating the optimal yield for a fish population.

The user interface can simply be opened with default parameter settings.
```{r, eval=FALSE}
library(shinyypr)
run_ypr_app()
```

The `run_ypr_app` function also has a single argument that allows the user to pass a valid ypr_population object, which populates the app parameter values on startup.

```{r, eval=FALSE}
library(ypr)
library(shinyypr)
adams <- adams_bt_03
adams_adjusted <- ypr_population_update(adams, "Rk" = 5, "Linf" = 140)
run_ypr_app(adams_adjusted)
```

`shinyypr` also ships with an RStudio addin. 

For more information see the `ypr` R package [Get Started](https://poissonconsulting.github.io/ypr/articles/ypr.html) vignette.

